Local to global N input modelling

### 2025-09-04 07_methods_and_supplementaries/07_methods_and_supplementaries.qmd

source(here("src/spatial_templates.R"))
source(here("src/model_functions.R"))

# Sys.setenv(TAR_PROJECT = "project_main")
base_path <- file.path("C:", "Users", "treimer", "Documents", "R-temp-files", "local_to_global_mariculture_modelling")
targets_store <- file.path(base_path, "targets", "_targets_individual")
farm_IDs <- tar_read(farm_IDs, store = targets_store)
b1 <- sample(length(farm_IDs), 100, replace = F)
b2 <- b1 + length(farm_IDs)
b3 <- b2 + length(farm_IDs)
b <- c(b1, b2, b3)
```

@@

# This is the full idealised year (2 years?) of temperature data
sst <- file.path(base_path, "data", "_general_data", "SST", "farm_SST_extracted.parquet") %>% read_parquet()

# This is the actual temperature curve for the farming period
farm_temp <- tar_read(example_individual, store = targets_store, branches = b1)
```

@@

species_params <- tar_read(species_params, store = targets_store)
pop_params <- tar_read(pop_params, store = targets_store)
weight <- tar_read(example_individual, store = targets_store, branches = b) %>% select(farm_ID, weight, days, prod_days, feed)
SGR <- tar_read(example_individual, store = targets_store, branches = b) %>% select(farm_ID, SGR, days, prod_days, feed)
FCR <- tar_read(example_individual, store = targets_store, branches = b) %>% select(farm_ID, FCR, days, prod_days, feed)

@@

df <- data.frame(water_temp = seq(-5, 30, 0.25))
df$resp <- exp(species_params['pk']*df$water_temp)

@@

feed_params_protein <- tar_read(feed_params_protein, store = targets_store)
feed_params_carbs <- tar_read(feed_params_carbs, store = targets_store)
feed_params_lipids <- tar_read(feed_params_lipids, store = targets_store)
```

@@

#c(b1, b2, b3))
ing_pot <- tar_read(example_individual, store = targets_store, branches = b1) %>% select(farm_ID, ing_pot, days, prod_days, feed)
ing_act <- tar_read(example_individual, store = targets_store, branches = b1) %>% select(farm_ID, ing_act, days, prod_days, feed)
food_prov <- tar_read(example_individual, store = targets_store, branches = b1) %>% select(farm_ID, food_prov, days, prod_days, feed)
```

@@

params <- tar_read(sens_all_params, store = targets_store)
pnames <- names(params)
```

>>>>

source(here("00_model_functions.R"))

# Sys.setenv(TAR_PROJECT = "project_main")
indi_store <- here() %>% file.path("04_targets_individual")
farm_IDs <- tar_read(farm_IDs, store = indi_store)
b1 <- sample(length(farm_IDs), 100, replace = F)
b2 <- b1 + length(farm_IDs)
b3 <- b2 + length(farm_IDs)
b <- c(b1, b2, b3)
```

@@

# This is the full idealised year (2 years?) of temperature data
sst <- here() %>% file.path("data", "_general_data", "SST", "farm_SST_extracted.parquet") %>% read_parquet()

# This is the actual temperature curve for the farming period
farm_temp <- tar_read(example_individual, store = indi_store, branches = b1)
```

@@

species_params <- tar_read(species_params, store = indi_store)
pop_params <- tar_read(pop_params, store = indi_store)
weight <- tar_read(example_individual, store = indi_store, branches = b) %>% select(farm_ID, weight, days, prod_days, feed)
SGR <- tar_read(example_individual, store = indi_store, branches = b) %>% select(farm_ID, SGR, days, prod_days, feed)
FCR <- tar_read(example_individual, store = indi_store, branches = b) %>% select(farm_ID, FCR, days, prod_days, feed)

@@

df <- data.frame(water_temp = seq(0, 30, 0.25))
df$resp <- exp(species_params['pk']*df$water_temp)

@@

feed_params_protein <- tar_read(feed_params_protein, store = indi_store)
feed_params_carbs <- tar_read(feed_params_carbs, store = indi_store)
feed_params_lipids <- tar_read(feed_params_lipids, store = indi_store)
```

@@

#c(b1, b2, b3))
ing_pot <- tar_read(example_individual, store = indi_store, branches = b1) %>% select(farm_ID, ing_pot, days, prod_days, feed)
ing_act <- tar_read(example_individual, store = indi_store, branches = b1) %>% select(farm_ID, ing_act, days, prod_days, feed)
food_prov <- tar_read(example_individual, store = indi_store, branches = b1) %>% select(farm_ID, food_prov, days, prod_days, feed)
```

@@

params <- tar_read(sens_all_params, store = indi_store)
pnames <- names(params)
```

### 2025-09-04 08_relative_N_inputs.qmd
Proper index of files

source("00_dirs.R")
feed_pal <- c("past" = "#E41A1C", "reference" = "#377EB8", "future" = "#4DAF4A")

@@

N_input <- output_cohorts_data_path %>% list.files(full.names = T) %>% 
  str_subset("allfarms") %>% 
  str_subset("P_excr") %>% 
  qs::qread() %>% 
  mutate(mean = mean * 6.25) %>% 
  group_by(farm_ID, feed) %>% 
  reframe(mean = sum(mean) * 10^-6) %>% 
  pivot_wider(names_from = feed, values_from = mean)

>>>>

here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
feed_pal <- c("past" = "#E41A1C", "reference" = "#377EB8", "future" = "#4DAF4A")

@@

N_input <- per_biomass_cohort_path %>% 
  list.files(full.names = T) %>% 
  str_subset("allfarms") %>% 
  str_subset("P_excr") %>% 
  qs::qread() %>% 
  mutate(mean = mean * 6.25) %>% 
  group_by(farm_ID, feed) %>% 
  reframe(mean = sum(mean) * 10^-6) %>% 
  pivot_wider(names_from = feed, values_from = mean)

### 2025-09-04 archive/08_manuscript/manuscript.qmd

### Composition

@@

* Composition does not change through time or with increasing biomass (because digestibility does not change with fish size or temeprature)

```{r composition-throughtime}
#| eval: false

excreted_all %>% 
  pivot_longer(names_to = "macro", values_to = "perc", cols = c("protein", "lipids", "carbohydrates")) %>% 
  mutate(macro = factor(macro, levels = c("protein", "lipids", "carbohydrates"))) %>% 
  group_by(farm_ID, feed, macro) %>% 
  reframe(sd = sd(perc) %>% set_units("d-1"),
          mean = mean(perc)) %>% 
  ggplot(aes(x = farm_ID, colour = feed, fill = feed, y = 100*mean, ymin = 100*(mean-sd), ymax = 100*(mean+sd))) +
  geom_point(size = 2) +
  geom_errorbar(width = 0.5) +
  scale_color_manual(values = feed_pal) +
  scale_fill_manual(values = feed_pal) +
  facet_grid(rows = vars(macro)) +
  theme_classic() +
  labs(x = "Macronutrient", y = "Mean composition of faeces")
```

>>>>

### Excreted composition

@@

```{r composition-throughtime}
excreted_all %>% 
  pivot_longer(names_to = "macro", values_to = "perc", cols = c("protein", "lipids", "carbohydrates")) %>% 
  mutate(macro = factor(macro, levels = c("protein", "lipids", "carbohydrates"))) %>% 
  group_by(farm_ID, feed, macro) %>% 
  reframe(sd = sd(perc) %>% set_units("d-1"),
          mean = mean(perc)) %>% 
  ggplot(aes(x = farm_ID, colour = feed, fill = feed, y = 100*mean, ymin = 100*(mean-sd), ymax = 100*(mean+sd))) +
  geom_point(size = 2) +
  geom_errorbar(width = 0.5) +
  scale_color_manual(values = feed_pal) +
  scale_fill_manual(values = feed_pal) +
  facet_grid(rows = vars(macro)) +
  theme_classic() +
  labs(x = "Macronutrient", y = "Mean composition of faeces")
```

### 2025-09-04 docs/manuscript.qmd

here("00_model_functions.R") %>% source()
```

@@

| Parameter | Value | Reference |
|:------:|:------:|:-----------:|
| $\alpha$             | `r unname(params['alpha'])`      | [@broekhuizen_modelling_1994] |
| $\epsilon_{P}$       | `r unname(params['epsprot'])`    | @baldan_r_2018 |
| $\epsilon_{L}$       | `r unname(params['epslip'])`     | @baldan_r_2018 |
| $\epsilon_{C}$       | `r unname(params['epscarb'])`    | @baldan_r_2018 |
| $\epsilon_{O_2}$     | `r unname(params['epsO2'])`      | @elliott_energy_1975 |
| $p_k$                | `r unname(params['pk'])`         | @macnaughton_using_2019 |
| $k_0$                | `r unname(params['k0'])`         | @macnaughton_using_2019 |
| $m$                  | `r unname(params['m'])`          | @broekhuizen_modelling_1994 | 
| $n$                  | `r unname(params['n'])`          | @baldan_r_2018 |
| $\beta C$            | `r unname(params['betac'])`      | @jonsson_thermal_2001 |
| $T_{max}$            | `r unname(params['Tma'])`        | @poletto_unusual_2017 | 
| $T_{opt}$            | `r unname(params['Toa'])`        | @jonsson_thermal_2001 | 
| $T_{min}$            | `r unname(params['Taa'])`        | @vadboncoeur_lowering_2023 | 
| $\omega$             | `r unname(params['omega'])`      | @baldan_r_2018 |
| $a$                  | `r unname(params['a'])`          | @van_tien_development_2016 |
| $k$                  | `r unname(params['k'])`          | @van_tien_development_2016 | 
| $eff$                | `r unname(params['eff'])`        | @uglem_does_2020 | 
| $\overline{W}$       | `r unname(params['meanW'])`      | @dempsey_estimating_2023 | 
| $\Delta{W}$          | `r unname(params['deltaW'])`     | @dempsey_estimating_2023 | |
| $\overline{I_{max}}$ | `r unname(params['meanImax'])`   | @lall_nutrition_2009 | 
| $\Delta{I_{max}}$    | `r unname(params['deltaImax'])`  | @lall_nutrition_2009 | 
| $\overline{F}$       | `r unname(params['overFmean'])`  | |
| $\Delta{F}$          | `r unname(params['overFdelta'])` | |
| $mort$               | `r unname(params['mortmyt'])`    | @tvete_towards_2023 |
: Model growth parameters for Atlantic salmon (for double-checking numbers and reference list only) {#tbl-params}

@@

```{r uneaten feed data}
#| code-summary: Load and prep uneaten feed data

uneaten_total <- farmrun_files %>% 
  purrr::map(function(f) {qs::qread(f)[["total_uneat_stat"]]}) %>% 
  bind_rows() %>% 
  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
  rename(uneat_mean = mean.x, biomass_mean = mean.y,
         uneat_sd = sd.x, biomass_sd = sd.y) %>% 
  mutate(uneat_sd = uneat_sd/uneat_mean,
         biomass_sd = biomass_sd/biomass_mean,
         uneat_biom_mean = uneat_mean/biomass_mean,
         uneat_biom_sd = sqrt(uneat_sd^2+biomass_sd^2)*uneat_biom_mean)
```

```{r uneaten feed analysis}
uneaten_total_stats <- uneaten_total %>% 
  group_by(feed, farm_ID) %>% 
  reframe(total = sum(uneat_biom_mean)) %>% 
  group_by(feed) %>% 
  reframe(min = minna(total),
          max = maxna(total),
          mean = meanna(total)) %>% 
  mutate(min = min %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
         max = max %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
         mean = mean %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1")) %>% 
  mutate(min = round(min,2),
         max = round(max,2),
         mean = round(mean,2))

uneaten_total_compare <- uneaten_total %>% 
  group_by(feed, farm_ID) %>% 
  reframe(total = sum(uneat_biom_mean)) %>% 
  pivot_wider(names_from = "feed", values_from = "total", id_cols = "farm_ID") %>% 
  mutate(diff_past = past-reference,
         diff_future = future-reference,
         diffperc_past = diff_past/reference,
         diffperc_future = diff_future/reference) %>% 
  dplyr::select(-c(reference, future, past)) %>% 
  pivot_longer(names_to = c("measure", "feed"), names_sep = "_", values_to = "value",
               cols = contains("diff"), names_transform = list(measure = as.factor, feed = as.factor)) %>% 
  group_by(feed, measure) %>% 
  reframe(min = minna(value),
          max = maxna(value),
          mean = meanna(value)) %>% 
  mutate(
    min = case_when(measure == "diffperc" ~ 100*min,
                    T ~ min %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
    max = case_when(measure == "diffperc" ~ 100*max,
                    T ~ max %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
    mean = case_when(measure == "diffperc" ~ 100*mean,
                     T ~ mean %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
    )
```

Total uneaten feed across a cohort (548 days) fed the reference feed ranged from 
`r uneaten_total_stats$min[uneaten_total_stats$feed == "reference"]` to 
`r uneaten_total_stats$max[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$ fish, with a mean of 
`r uneaten_total_stats$mean[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$ fish. 
Differences between the feeds were very small, but slightly less feed was left uneaten in the reference scenario (@fig-total-uneaten-perday). Uneaten feed in the past scenario ranged from 
`r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` to 
`r uneaten_total_stats$max[uneaten_total_stats$feed == "past"]` g kg$^{-1}$ fish (mean of 
`r uneaten_total_stats$mean[uneaten_total_stats$feed == "past"]` g kg$^{-1}$ fish) while uneaten feed in the future scenario ranged from 
`r uneaten_total_stats$min[uneaten_total_stats$feed == "future"]` to 
`r uneaten_total_stats$max[uneaten_total_stats$feed == "future"]` g kg$^{-1}$ (mean of 
`r uneaten_total_stats$mean[uneaten_total_stats$feed == "future"]`  g kg$^{-1}$ fish).

```{r fig-total-uneaten-perday}
#| fig-cap: |
#|   Feed left uneaten when fish are fed the reference (blue), past (red) or future (green) feed. Countries are arranged by descending mean latitude.

uneaten_total %>% 
  merge(farms_geometry, by = "farm_ID") %>% 
  mutate(uneat_biom_mean = uneat_biom_mean %>% set_units("g g_fish-1 d-1") %>% set_units("g kg_fish-1 d-1"),
         country = factor(country, levels = sorted_countries)) %>% 
  ggplot(aes(x = country, y = uneat_biom_mean, fill = feed)) +
  geom_boxplot() +
  prettyplot() +
  scale_fill_manual(values = feed_pal) +
  labs(y = "Uneaten feed", x = "Country")
```

```{r uneaten composition}
#| eval: false

uneaten_P <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["P_uneat_stat"]]}) %>% bind_rows()
uneaten_L <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["L_uneat_stat"]]}) %>% bind_rows()
uneaten_C <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["C_uneat_stat"]]}) %>% bind_rows()

uneaten_all <- uneaten_total %>% 
  select(-contains("biom")) %>% 
  merge(uneaten_P, by = c("farm_ID", "feed", "t")) %>% 
  merge(uneaten_L, by = c("farm_ID", "feed", "t")) %>% 
  merge(uneaten_C, by = c("farm_ID", "feed", "t")) %>% 
  select(-c(contains("sd")))
```

The composition of the uneaten feed is (obviously) the same as the total feed composition detailed in (@sec-feeds).

## Excreted faeces

```{r excreted faeces data}
#| code-summary: Load and prep all excretion data

# The following reads in all the total excretion data and converts the mean and sd values into values/biomass
excreted_total <- farmrun_files %>% 
  purrr::map(function(f) {qs::qread(f)[["total_excr_stat"]]}) %>% 
  bind_rows() %>% 
  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
  rename(excr_mean = mean.x, biomass_mean = mean.y,
         excr_sd = sd.x, biomass_sd = sd.y) %>% 
  mutate(excr_sd = excr_sd/excr_mean,
         biomass_sd = biomass_sd/biomass_mean,
         excr_biom_mean = excr_mean/biomass_mean,
         excr_biom_sd = sqrt(excr_sd^2+biomass_sd^2)*excr_biom_mean)

excreted_total_stats <- excreted_total %>% 
  group_by(feed, farm_ID) %>% 
  reframe(total = sum(excr_biom_mean)) %>% 
  group_by(feed) %>% 
  reframe(min = minna(total),
          max = maxna(total),
          mean = meanna(total)) %>% 
  mutate(min = min %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
         max = max %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
         mean = mean %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1")) %>% 
  mutate(min = round(min,2),
         max = round(max,2),
         mean = round(mean,2))
```

### Amount

Overall, total excretion was lowest when when fish were fed the past feed and highest when fish were fed the reference feed (@fig-total-excreted-perday). 
Total excreted faeces across a cohort (548 days) in the reference scenario ranged from `r excreted_total_stats$min[excreted_total_stats$feed == "reference"]` to 
`r excreted_total_stats$max[excreted_total_stats$feed == "reference"]` g kg$^{-1}$ fish d$^{-1}$, with a mean of 
`r excreted_total_stats$mean[excreted_total_stats$feed == "reference"]`.
Total excreted faeces across a cohort in the past scenario ranged from 
`r excreted_total_stats$min[excreted_total_stats$feed == "past"]` to 
`r excreted_total_stats$max[excreted_total_stats$feed == "past"]` g kg$^{-1}$ fish d$^{-1}$ (mean of 
`r excreted_total_stats$mean[excreted_total_stats$feed == "past"]` g kg$^{-1}$ fish d$^{-1}$).
Total excreted faeces across a cohort in the future scenario ranged from 
`r excreted_total_stats$min[excreted_total_stats$feed == "future"]` to 
`r excreted_total_stats$max[excreted_total_stats$feed == "future"]` g kg$^{-1}$ fish d$^{-1}$ (mean of 
`r excreted_total_stats$mean[excreted_total_stats$feed == "future"]` g kg$^{-1}$ fish d$^{-1}$).

```{r fig-total-excreted-perday}
#| fig-cap: |
#|   Feed left uneaten when fish are fed the reference (blue), past (red) or future (green) feed. Countries are arranged by descending mean latitude.

>>>>

here("00_model_functions.R") %>% source()

remove_unit("gN")
install_unit("gN", "6.25 g") # 1/6.25
```

@@

| Parameter | Value | Reference |
|:------:|:------:|:-----------:|
| $\alpha$             | `r unname(params['alpha'])`      | @broekhuizen_modelling_1994 |
| $\epsilon_{P}$       | `r unname(params['epsprot'])`    | @baldan_r_2018 |
| $\epsilon_{L}$       | `r unname(params['epslip'])`     | @baldan_r_2018 |
| $\epsilon_{C}$       | `r unname(params['epscarb'])`    | @baldan_r_2018 |
| $\epsilon_{O_2}$     | `r unname(params['epsO2'])`      | @elliott_energy_1975 |
| $p_k$                | `r unname(params['pk'])`         | @macnaughton_using_2019 |
| $k_0$                | `r unname(params['k0'])`         | @macnaughton_using_2019 |
| $m$                  | `r unname(params['m'])`          | @broekhuizen_modelling_1994 | 
| $n$                  | `r unname(params['n'])`          | @baldan_r_2018 |
| $\beta C$            | `r unname(params['betac'])`      | @jonsson_thermal_2001 |
| $T_{max}$            | `r unname(params['Tma'])`        | @poletto_unusual_2017 | 
| $T_{opt}$            | `r unname(params['Toa'])`        | @jonsson_thermal_2001 | 
| $T_{min}$            | `r unname(params['Taa'])`        | @vadboncoeur_lowering_2023 | 
| $\omega$             | `r unname(params['omega'])`      | @baldan_r_2018 |
| $a$                  | `r unname(params['a'])`          | @van_tien_development_2016 |
| $k$                  | `r unname(params['k'])`          | @van_tien_development_2016 | 
| $eff$                | `r unname(params['eff'])`        | @uglem_does_2020 | 
| $\overline{W}$       | `r unname(params['meanW'])`      | @dempsey_estimating_2023 | 
| $\Delta{W}$          | `r unname(params['deltaW'])`     | @dempsey_estimating_2023 | |
| $\overline{I_{max}}$ | `r unname(params['meanImax'])`   | @lall_nutrition_2009 | 
| $\Delta{I_{max}}$    | `r unname(params['deltaImax'])`  | @lall_nutrition_2009 | 
| $\overline{F}$       | `r unname(params['overFmean'])`  | |
| $\Delta{F}$          | `r unname(params['overFdelta'])` | |
| $mort$               | `r unname(params['mortmyt'])`    | @tvete_towards_2023 |
: Model growth parameters for Atlantic salmon (for double-checking numbers and reference list only) {#tbl-params}

@@

```{r inputs data}
#| code-summary: Load and prep uneaten feed and faeces data (keep in g faeces/feed)

mass_inputs_ts <- find_read(data_analysis_path, "all_waste_inputs")
mass_inputs_end <- find_read(data_analysis_path, "sumtotal_waste_inputs.qs")
N_inputs_ts <- find_read(data_analysis_path, "all_N_inputs")
N_inputs_end <- find_read(data_analysis_path, "sumtotal_N_inputs")
```

```{r inputs stats through time}
#| eval: false
#| code-summary: Show how inputs (mass and N) change through time (across all farms)

mass_inputs_ts
N_inputs_ts

# Through time
inputs_stats_ts <- inputs_df %>%
  group_by(feed, t, measure) %>% 
  reframe(min = minna(mean),
          max = maxna(mean),
          sd = sdna(mean) %>% set_units("g"),
          mean = meanna(mean))

inputs_stats_rel_ts <- inputs_rel_df %>% 
  group_by(feed, t, measure) %>% 
  reframe(min = minna(mean),
          max = maxna(mean),
          sd = sdna(mean) %>% set_units("g g_fish-1"),
          mean = meanna(mean))

# Total (at production end)
inputs_stats_end <- inputs_df %>% 
  group_by(feed, measure, farm_ID) %>% 
  reframe(mean = sumna(mean)) %>% 
  group_by(feed, measure) %>% 
  reframe(min = minna(mean),
          max = maxna(mean),
          sd = sdna(mean) %>% set_units("g"),
          mean = meanna(mean))

inputs_stats_rel_end <- inputs_rel_df %>% 
  group_by(feed, measure, farm_ID) %>% 
  reframe(mean = sumna(mean)) %>% 
  group_by(feed, measure) %>% 
  reframe(min = minna(mean),
          max = maxna(mean),
          sd = sdna(mean) %>% set_units("g g_fish-1"),
          mean = meanna(mean))

inputs_stats_rel_end_diff <- inputs_rel_df %>% 
  group_by(feed, measure, farm_ID) %>% 
  reframe(mean = sumna(mean)) %>% 
  pivot_wider(names_from = feed, values_from = mean) %>% 
  mutate(future = (future-reference)/reference,
         past = (past-reference)/reference) %>% 
  select(-reference) %>% 
  pivot_longer(cols = c(past, future), names_to = "feed", values_to = "diff") %>% 
  mutate(feed = factor(feed, levels = c("past", "future"))) %>% 
  group_by(feed, measure) %>% 
  reframe(min = minna(diff),
          max = maxna(diff),
          sd = sdna(diff),
          mean = meanna(diff))

# Pull key values (uneaten feed)
u_stmin1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(min)
u_stmax1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(max)
u_stmean1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(mean)
u_stmin2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(min)
u_stmax2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(max)
u_stmean2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(mean)
u_stmin3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(min)
u_stmax3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(max)
u_stmean3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(mean)

# Convert past and future values to % change values
u_stmin2 <- (100*u_stmin2) %>% round(2)
u_stmax2 <- (100*u_stmax2) %>% round(2)
u_stmean2 <- (100*u_stmean2) %>% round(2)
u_stmin3 <- (100*u_stmin3) %>% round(2)
u_stmax3 <- (100*u_stmax3) %>% round(2)
u_stmean3 <- (100*u_stmean3) %>% round(2)

u_stmin1 <- u_stmin1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
u_stmax1 <- u_stmax1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
u_stmean1 <- u_stmean1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)

# Pull key values (excreted faeces)
e_stmin1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(min)
e_stmax1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(max)
e_stmean1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(mean)
e_stmin2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(min)
e_stmax2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(max)
e_stmean2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(mean)
e_stmin3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(min)
e_stmax3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(max)
e_stmean3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(mean)

# Convert past and future values to % change values
e_stmin2 <- (100*e_stmin2) %>% round(2)
e_stmax2 <- (100*e_stmax2) %>% round(2)
e_stmean2 <- (100*e_stmean2) %>% round(2)
e_stmin3 <- (100*e_stmin3) %>% round(2)
e_stmax3 <- (100*e_stmax3) %>% round(2)
e_stmean3 <- (100*e_stmean3) %>% round(2)

e_stmin1 <- e_stmin1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
e_stmax1 <- e_stmax1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
e_stmean1 <- e_stmean1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
```

```{r waste inputs stats total}
#| code-summary: Show how waste inputs change in total (at the end of a production period) across all farms

mass_inputs_sep <- mass_inputs_end %>% 
  mutate(waste_per_biomass = set_units(total/biomass_total, "g kg_fish-1")) %>% 
  dplyr::select(-c(total, biomass_total)) %>% 
  pivot_wider(names_from = measure, values_from = waste_per_biomass) %>% 
  mutate(total = excr+uneat) %>% 
  pivot_longer(names_to = "measure", values_to = "waste_per_biomass", cols = c(total, excr, uneat), names_transform = list(measure = as.factor)) %>% 
  group_by(feed, measure) %>% 
  reframe(mean_wpb = meanna(waste_per_biomass),
          mean_wpb = sdna(waste_per_biomass) %>% set_units("g kg_fish-1"),
          min_wpb = minna(waste_per_biomass),
          max_wpb = maxna(waste_per_biomass))

twi_min <- mass_inputs_sep$min_wpb[mass_inputs_sep$measure == "total"] %>% round(2)
twi_max <- mass_inputs_sep$max_wpb[mass_inputs_sep$measure == "total"] %>% round(2)
twi_mean <- mass_inputs_sep$mean_wpb[mass_inputs_sep$measure == "total"] %>% round(2)

# There were only very small differences in total uneaten feed between the different feeds, with the past feed increasing uneaten feed by `r u_stmin2`-`r u_stmax2`%  (mean of `r u_stmean2`%) and the future feed increasing uneaten feed by `r u_stmin3`-`r u_stmax3`%  (mean of `r u_stmean3`%).

# * Total excreted faeces across a cohort fed the reference feed ranged from `r e_stmin1` to `r e_stmax1` g kg$^{-1}$ fish, with a mean of `r e_stmean1` g kg$^{-1}$ fish. 
# * Past feed decreased excreted faeces by `r -1*e_stmin2`-`r -1*e_stmax2`%  (mean of `r -1*e_stmean2`%) 
# * Future feed increased excreted faeces by `r e_stmin3`-`r e_stmax3`%  (mean of `r e_stmean3`%)
```

* Total waste inputs across a single production period of fish fed the reference feed ranged from `r twi_min[1]` to `r twi_max[1]` g kg$^{-1}$ fish, with a mean of `r twi_mean[1]` g kg$^{-1}$ fish.
* Total waste inputs across a single production period of fish fed the past feed ranged from `r twi_min[2]` to `r twi_max[2]` g kg$^{-1}$ fish, with a mean of `r twi_mean[2]` g kg$^{-1}$ fish.
* Total waste inputs across a single production period of fish fed the future feed ranged from `r twi_min[3]` to `r twi_max[3]` g kg$^{-1}$ fish, with a mean of `r twi_mean[3]` g kg$^{-1}$ fish.

```{r fig-waste-inputs-total}
#| fig-cap: | 
#|   Total waste intputs (uneaten feed + excreted faeces) across the whole production period at each farm location.
#| fig-width: 9.5

mass_inputs_sep_geometry <- mass_inputs_end %>% 
  mutate(waste_per_biomass = set_units(total/biomass_total, "g kg_fish-1")) %>% 
  dplyr::select(-c(total, biomass_total)) %>% 
  pivot_wider(names_from = measure, values_from = waste_per_biomass) %>% 
  mutate(total = excr+uneat) %>% 
  pivot_longer(names_to = "measure", values_to = "waste_per_biomass", cols = c(total, excr, uneat), names_transform = list(measure = as.factor)) %>% 
  group_by(farm_ID, feed, measure) %>% 
  reframe(mean_wpb = meanna(waste_per_biomass),
          sd_wpb = sdna(waste_per_biomass) %>% set_units("g kg_fish-1"),
          min_wpb = minna(waste_per_biomass),
          max_wpb = maxna(waste_per_biomass)) %>% 
  merge(farms_geometry, by = "farm_ID")

mass_inputs_robinson <- mass_inputs_sep_geometry %>% 
  filter(feed == "reference" & measure == "total") %>% 
  mutate(mean_wpb = mean_wpb %>% drop_units()) %>% 
  st_sf() %>% 
  st_transform(crs = "+proj=robin")

ggplot() +
  geom_sf(data = graticules, color = "gray80", size = 0.3) +
  geom_sf(data = worldmap, fill = "white", color = "dimgray") +
  geom_sf(data = mass_inputs_robinson, aes(color = mean_wpb), size = 1) +
  coord_sf() +
  scale_color_viridis_c(option = "turbo") +
  guides(col = guide_colourbar(
    title = expression("Mean waste inputs (g g fish"^-1*")"),
    direction = "horizontal", position = "bottom",
    label.position = "bottom", title.position = "top", 
    title.vjust = 1, title.hjust = 0.5,
    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
    barwidth = 25,barheight = 1.5
  )) +
  geom_sf(data = boxes_robinson, fill = NA, color = "darkred", size = 1.65) +
  geom_sf_text(data = labels_robinson, aes(label = letter), 
               color = "darkred", size = 5, fontface = "bold", 
               hjust = 0.5, vjust = 0.5) +
  theme_void()
```

```{r patchwork-waste-map-mercator}
#| fig-cap: |
#|   Example of a patchwork
#| fig-height: 9
#| fig-width: 9.5

mass_inputs_patch <- mass_inputs_sep_geometry %>% 
  filter(feed == "reference" & measure == "total") %>% 
  mutate(mean_wpb = mean_wpb %>% drop_units())

p1 <- ggplot() +
  geom_sf(data = worldmap, fill = "white", color = "dimgray") +
  geom_sf(data = mass_inputs_patch, aes(color = mean_wpb, geometry = geometry), size = 2) +
  coord_sf() +
  scale_color_viridis_c(option = "turbo") +
  guides(col = guide_colourbar(
    title = expression("Mean waste inputs (g g fish"^-1*")"),
    direction = "vertical", position = "right",
    label.position = "right", title.position = "top", 
    title.vjust = 1, title.hjust = 0.5,
    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1.5,
    barwidth = 1.5, barheight = 20,
  )) +
  prettyplot() +
  labs(y = "Latitude", x = "Longitude")

```{r fig-total-excreted-perday}
#| eval: false
#| fig-cap: |
#|   Feed left uneaten when fish are fed the reference (blue), past (red) or future (green) feed. Countries are arranged by descending mean latitude.
